\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{gfsdidot} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
	pdftitle={CV},
	pdfpagemode=FullScreen,
}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Brandon J. Klein} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Ph.D. Candidate}
\moveleft.5\hoffset\centerline{bklein6@jhu.edu}
\moveleft.5\hoffset\centerline{(980) 475-2222}

\begin{resume}

\section{EDUCATION} 
{\bf Johns Hopkins University \hfill 2024 - Current}
\begin{itemize}
	\item Ph.D. in Theoretical Condensed Matter Physics, Expected 2027
	\item Master of Arts in Physics, 2022 - 2024
	\item Advisor: Daniel A. Beller
	\item Research Interests: nematic liquid crystals, soft condensed matter physics, active matter, theoretical biophysics.
	\item Relevant Coursework: Advanced Statistical Mechanics, Numerical Methods, Condensed Matter Theory, Electrodynamics, Quantum Mechanics.
\end{itemize}
{\bf Rensselaer Polytechnic Institute  \hfill 2018 - 2022}
\begin{itemize}
    \item Bachelor of Science in Physics 
    \item Bachelor of Science in Computer Science
    \item Summa Cum Laude
    \item Relevant Coursework: Design and Analysis of Algorithms, Computational Physics, Machine Learning from Data.
\end{itemize}


\section{PUBLICATIONS}
\begin{itemize}
  \item {\bf Klein, Brandon} and Soto Franco, Alejandro, and Sabbir, Md Mainul Hasan and Deutsch, Matthew J. and Selinger, Robin L.B. and Mitchell, Kevin A. and Beller, Daniel A., {\it Limits of Topological Entropy Production in Confined Active Nematics}, {\it In Preparation}, 2025.
  \item Mitchell, Kevin A. and Sabbir, Md Mainul Hasan and Geumhan, Kevin and Smith, Spencer A. and {\bf Klein, Brandon} and Beller, Daniel A., {\it Maximally mixing active nematics}, {Phys. Rev. E}, 2024, 109, 014606.
  \item {\bf Klein, Brandon} and Liang, Liangbo and Meunier, Vincent, {\it Low-Frequency Raman Active Modes of Twisted Bilayer MoS$_2$}, {Journal of Physics: Condensed Matter}, 2024, 36, 365301.


% \begin{itemize}
% 	\item Contributed to development of hydrodynamics simulation to study topological defect dynamics in active nematic liquid crystals.
% 	\item Developed scheme for simulating complex boundaries to study confined active nematics. Work presented in poster session at University of Massachusetts Amherst Soft Solids and Complex Fluids Summer School 2023.
% 	\item Simulated an experimentally realizable method for stabilizing periodic defect motion on arbitrarily large tilings. Findings described in 
% 	{Mitchell et al., {\it Maximally Mixing Active Nematics}, PRE (2024)}
% \end{itemize}
% {\bf Quantum Monte Carlo \hfill Fall 2022}\\
% {\sl Advisor: Yi Li}
% \begin{itemize}
% 	\item Investigated thermodynamic properties and magnetic phase transitions of an XY class p-orbital system using a world-line Quantum Monte Carlo scheme.
% 	\item Described the dynamics of KT transition and associated correlation functions.
% 	\item Analyzed the low temperature behavior of magnetic susceptibilities.
% \end{itemize}
% {\bf NSF REU on Twisted Bilayer Mos$_2$ \hfill Summer 2021 - Summer 2022}\\
% {\sl Interdisciplinary Computational Material Physics (Advisor: Vincent Meunier)}
% \begin{itemize}
%     \item Investigated the phonon band structure of twisted bilayer MoS$_2$ using molecular dynamics approaches in LAMMPS by implementing a ReaxFF and Kolmogorov-Crespi potential for structures of interest.
%     \item Classified the interlayer breathing and shear modes of MoS$_2$ and identified twisting encouraged band splitting in first Brillouin Zone.
%     \item Summarized findings in a research poster presented at an undergraduate symposium and a final report for REU program.
% \end{itemize}
% {\bf Thin Film Surface Morphology \hfill Spring 2020 - Spring 2021}\\
% {\sl Advisor: Toh-Ming Lu}
% \begin{itemize}
%     \item Investigated high pressure chemical vapor depositions using Monte Carlo methods and constructed an analytical model for measuring amplitude decay over arbitrary substrates under ballistic and solid-on-solid deposition types.
%     \item Used Python with Numpy, Scipy, and Pandas data analysis to determine the efficacy of depositions in achieving conformal coating and determined the threshold pressures for optimizing coating process on various substrates.  
\end{itemize}

\section{EXPERIENCE}
\begin{itemize}
 \item Graduate Teaching Assistant \hfill Fall 2022 - Spring 2023, Fall 2024
 \subitem{-Physics 1, Physics 2 at Johns Hopkins University}
 \item NSF REU \hfill Summer 2021 - Summer 2022
 \subitem{-Interdisciplinary Computational Material Physics, Advisor: Vincent Meunier}
 \item Software Engineering Intern at GlobalFoundries \hfill Fall 2020
\subitem{-Optical Proximity Correction Intern, Supervisor: Tamer Desouky}
\item Undergraduate Facilitator and Senior Mentor \hfill Spring 2019 - Fall 2021
\subitem{-Honors Physics 1, Physics 1, Foundations of Computer Science, Theoretical Mechanics, Thermodynamics \& Statistical Mechanics at RPI}
\end{itemize}

\section{CONFERENCES AND TALKS}
\begin{itemize}
    \item Gordon Research Conference on Liquid Crystals, {\it invited speaker at seminar}, 2025
    \item APS March Meeting, {\it oral contribution}, 2025
    \item University of Pennsylvania Soft Matter Center Kickoff, {\it poster presentation}, 2024
    \item International Liquid Crystal Conference, {\it oral contribution}, 2024
    \item Banff International Research Station Workshop on Active Matter, {\it invited speaker}, 2024
    \item APS March Meeting, {\it oral contribution}, 2024
    \item University of Massachusetts Amherst Soft Solids and Complex Fluids Summer School, {\it poster presentation}, 2023
\end{itemize}
    
\section{AWARDS}
\begin{itemize}
\item RPI Leadership Award
\item RPI Bicentennial Award
    \item Nadia Trinkala Service Award (for contributions to the city of Troy).
    \item Upsilon Pi Epsilon (UPE) International Computing and Information Disciplines Honor Society.
    \end{itemize}


\section{TECHNICAL SKILLS} 
\begin{itemize}
    \item C, C++, Java, Javascript, MIPS, Perl, Python, Rust.
    \item Data visualization and analysis.
    \item Unix, SSH, Bamboo, and Git.
    \item Monte Carlo methods.
    \item Numeric PDE methods.
    \item Machine learning in PyTorch, Keras, and Sklearn. 
    \item Limited working proficiency in Mandarin Chinese.
\end{itemize} 
\section{REFERENCES}
\begin{itemize}
    \item Daniel A. Beller at Johns Hopkins University:\\
    d.a.beller@jhu.edu
    \item Yi Li at Johns Hopkins University:\\
    yili.phys@jhu.edu
    \item Vincent Meunier at Pennsylvania State University:\\
    Vincent.Meunier@psu.edu
\end{itemize}

\end{resume}

\end{document}
